Analysis of diagnostic programm performances
========================================================

# Performance Analysis

## Summary
```{r}
datas=read.csv2("../test/temp.csv",sep=";",colClasses=c("NULL","NULL","factor","NULL","NULL","factor","factor","numeric","factor","factor","numeric","numeric","numeric","numeric"))
#protocol  Success	formula_human	formula_cpu	Ininterp_human	Ininterp_cpu	AnomaliesCount	problem	problemSerie
head(datas)
summary(datas)
```

## some tables
```{r}
table(datas$Success)
datas2<-datas
datas2$AnomaliesCount[datas2$AnomaliesCount>=4] <- ">3"
datas2$AnomaliesCount<-as.factor(datas2$AnomaliesCount)
datas2$AnomaliesCount=factor(datas2$AnomaliesCount,levels(datas2$AnomaliesCount)[c(2:5,1)])
table(datas2$AnomaliesCount,datas2$Ininterp_cpu)
t2=table(datas2$Ininterp_cpu,datas2$Success,dnn=c("ininterpretable","succès"))
t3=table(datas2$AnomaliesCount,datas2$Success,dnn=c("Valeurs du compteur","succès"))
t3
prop.table(t3,1)
prop.table(t3)
prop.table(t2,1)
prop.table(t2,2)
prop.table(t2)
nrow(datas)
table(datas2$Success,datas2$problemSerie)
datas3<-datas
t=table(datas$Success)
t/margin.table(t)
t3=table(datas$Ininterp_cpu)
t3/margin.table(t3)
```
### Relation between different categories of anomalies and success
```{r}
t3_doubts=table(datas2$Success,datas2$DoubtSelect,dnn=c("Valeurs du compteur","succès"))
t3_doubts
```

### Relation between different categories of anomalies and success
```{r}
t3_hub=table(datas2$Success,datas2$DoubtNumber,dnn=c("Valeurs du compteur","succès"))
t3_hub
```

# Experimentation
Humans had to pick which diagnosis sounds the better along with their confidence level.
We study the dataset.

## Summary
```{r}
datasComp=read.csv2("../test/comparisonHumanComp.csv",sep=";",colClasses=c("NULL","factor","factor","factor","factor","factor","factor","factor","NULL","factor","NULL","NULL","factor","factor","numeric","factor","factor","numeric","numeric","numeric","numeric"))
#protocol  Success  formula_human	formula_cpu	Ininterp_human	Ininterp_cpu	AnomaliesCount	problem	problemSerie
head(datasComp)
datasComp=head(datasComp,100) # only a part has been used in the study
summary(datasComp)
```

```{r}
datasComp$votesForHuman=as.numeric(datasComp$selectionE==datasComp$humanSelection)+as.numeric(datasComp$selectionV==datasComp$humanSelection)+as.numeric(datasComp$selectionB==datasComp$humanSelection)
table(datasComp$votesForHuman)
```

## repartition of votes

```{r}
table(as.factor(datasComp$votesForHuman))
```

## correspondance with anomalies
```{r}
datasComp$AnomaliesCount[datasComp$AnomaliesCount>=2] <- ">1"
datasComp$AnomaliesCount<-as.factor(datasComp$AnomaliesCount)
datasComp$AnomaliesCount=factor(datasComp$AnomaliesCount,levels(datasComp$AnomaliesCount)[c(2:4,1)])
table(datasComp$AnomaliesCount,datasComp$votesForHuman)
```
